How to Avoid OOTA Without Really Trying

### 2024-09-13 paper/ootavacuous.tex
ootavacuous: Untangle quasi-volatile sentence in abstract
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

	We focus on shared-memory programs and C++ implementations based
	on traditional compilers and hardware, including CPUs and GPGPUs,
	thus enabling analysis of semantic dependencies and OOTA behaviors
	by means of existing hardware models.
	We show that these models' constraints prevent OOTA cycles from
	occurring in undefined-behavior-free C++ programs running on
	such implementations, provided the cycles involve only volatile
	atomics.
	For implementations doing only per-thread analysis and
	optimization, we accommodate nonvolatile atomics by defining
	``quasi-volatile'' behavior, adherence to which avoids situations
	in which arithmetic-expression evaluation involving atomic
	accesses could otherwise violate the standard.

>>>>

	We focus on shared-memory programs and C++ implementations based
	on traditional compilers and hardware, including CPUs and GPGPUs,
	thus enabling analysis of semantic dependencies and OOTA behaviors
	by means of existing hardware models.
	We show that these models' constraints prevent OOTA cycles from
	occurring in undefined-behavior-free C++ programs running on
	such implementations, provided the cycles involve only volatile
	atomics.
	We accommodate nonvolatile atomics by defining ``quasi-volatile''
	behavior that enables implementations doing per-thread analysis
	and optimization to not only avoid OOTA, but also to avoid 
	incorrectly evaluating arithmetic expressions involving atomic
	accesses.
